```{r}
library(p8105.datasets)
library(dplyr)
library(ggplot2)
library(tidyr)

data(nyc_airbnb)

nyc_airbnb <- 
  nyc_airbnb %>%
  rename (borough = neighbourhood_group) %>% 
  mutate(stars = review_scores_location/2)

nyc_airbnb
```

##Brainstorm questions 
- Where are AirBNBs expensive?
  - Borough? Neighborhood? 
  - Do other factors (room type) affect price? What about rating?
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How many apartments are run by one host? 
  - Does that affect price? 
  - Does that vary by neighborhood?
- Where are AirBNBs?
  - Borough? Neighborhood? 
  - Lat and long? 
  
```{r}
nyc_airbnb %>% 
  group_by(borough) %>% 
  summarise(average = mean(price)) %>% 
  arrange(desc(average))

nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarise(average = mean(price)) %>% 
  arrange(desc(average))

nyc_airbnb %>% 
  group_by(stars) %>% 
  summarise(average = mean(price)) %>% 
  arrange(desc(average))

min_nights_df <- nyc_airbnb %>% 
  group_by(minimum_nights) %>% 
  summarise(average = mean(price)) %>% 
  arrange(minimum_nights) %>% 
  filter(minimum_nights <= 50)

ggplot(min_nights_df, aes(x = minimum_nights, y= average)) + 
  geom_bar(stat= "identity")

host_listings_df <- nyc_airbnb %>% 
  group_by(calculated_host_listings_count) %>% 
  summarise(average = mean(price)) %>% 
  arrange(calculated_host_listings_count) 

ggplot(host_listings_df, aes(x = calculated_host_listings_count, y= average)) + 
  geom_bar(stat= "identity")
```

```{r}
nyc_airbnb %>% 
  count(borough) %>% 
  arrange(desc(n))
```

```{r}
nyc_airbnb %>% 
  group_by(borough, neighbourhood) %>% 
  summarise(mean_price = mean(price)) %>% 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb %>% 
  group_by(borough, neighbourhood) %>% 
  summarise(median_price = median(price)) %>% 
  arrange(desc(median_price))
```

```{r}
nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarise(mean_price = mean(price)) %>% 
  arrange(desc(mean_price)) %>%
  pivot_wider(
    names_from = room_type, 
    values_from = mean_price
  )
```

```{r}
nyc_airbnb %>% 
  filter(price <1000, room_type == "Entire home/apt") %>%
  ggplot(aes(x = price)) + 
  geom_histogram() + 
  facet_grid(. ~borough)
```

```{r}
nyc_airbnb %>% 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarise(
    n_apt = n(), 
    mean_price = mean(price)) %>% 
  arrange(desc(mean_price)) 

```